Implementing simplified INLA into `aghq`

### 2022-10-19 src/dev_sinla/sinla.Rmd
Add some tabs for checks and multiple ways of doing things

## Reproducing output from `h`

As a check, we would like to reproduce `h` using the right hand side of Equation \@ref(eq:pthetagiveny).
To do this, we start by creating an objective function `f` (see Appendix for the `TMB` template) to evaluate $- \log p(x, \theta, y)$ (without any Laplace approximations!).
This is what we will be using for the numerator of Equation \@ref(eq:pthetagiveny):

@@

@@

@@

### Method 1: Safe exponential then trapezoid rule

@@

### Method 2: logSumExp to calculate the log normalising constant

@@

norm_trapezoid_log <- trapezoid_rule_log(df$logpost, spacing)
df$post_norm_alt <- exp(df$logpost - norm_trapezoid_log)

plot3 <- plot2 +
  geom_line(data = df, aes(x = phi_prev_i, y = post_norm, col = "Laplace"), size = 1)

@@

The two ways of calculating the normalised posterior are the same up to numerical error:

```{r}
max(df$post_norm - df$post_norm_alt)
```

@@

...
So perhaps it's barely better than the Gaussian, but not really getting the real problem here.
Hypothesis would be that it's because we're doing empirical Bayes, and with more than one hyperparameter grid point we would do better.

>>>>

cowplot::plot_grid(plot(mean), image(Q), nrow = 1)
```

## Additional checks {.tabset .tabset-fade}

### Description

These tabs contain additional sanity checks used to build understanding.
Feel free to skip them.

### Reproducing output from `h`

We would like to reproduce `h` using the right hand side of Equation \@ref(eq:pthetagiveny).
To do this, we start by creating an objective function `f` (see Appendix for the `TMB` template) to evaluate $- \log p(x, \theta, y)$ (without any Laplace approximations!).
This is what we will be using for the numerator of Equation \@ref(eq:pthetagiveny):

@@

###

@@

## $\tilde p(x_i \, | \, y)$ {.tabset .tabset-fade}

@@

### Safe exponential then trapezoid rule

@@

### `logSumExp` to calculate the log normalising constant

@@

norm_trapezoid_log <- trapezoid_rule_log(df$logpost, spacing)
df$post_norm_alt <- exp(df$logpost - norm_trapezoid_log)
```

###

The two ways of calculating the normalised posterior above are the same up to numerical error:

```{r}
max(abs(df$post_norm - df$post_norm_alt))
```

We now add our Laplace approximation to the existing joint Gaussian marginal and MCMC results:

```{r}
plot3 <- plot2 +
  geom_line(data = df, aes(x = phi_prev_i, y = post_norm, col = "Laplace"), size = 1)

@@

@@

One thing to take into account is that we're doing empirical Bayes, and things might be improved by using more integration points.
